Synthesizing Symmetric Lenses

### 2019-02-28 papers/SymmetricLenses/main.tex
remove comments

Formally, we characterize the expressiveness of simple symmetric lenses by
proving that they are exactly the symmetric lenses
that satisfy an intuitive property called \emph{forgetfulness}.  We also show
they are expressive enough for many practical uses by adding simple
symmetric lenses to 
the Boomerang language~\cite{boomerang} and applying them to a range of
real-world applications.  This exercise also demonstrates that simple
symmetric lenses can coexist with, and be extended by, other advanced lens features
provided by Boomerang, including {\em quotient
  lenses}~\cite{quotientlenses,maina+:quotient-synthesis} and {\em matching
  lenses}~\cite{matchinglenses}.\bcp{How does it demonstrate this?  Did we
  actually {\em use} symmetric quotient or matching lenses for anything?  Or
are we just observing that these features can coexist in the same
implementation even if using them together might not make sense?}
\afm{Good point, updated.}

>>>>

Formally, we characterize the expressiveness of simple symmetric lenses by
proving that they are exactly the symmetric lenses
that satisfy an intuitive property called \emph{forgetfulness}.  We also show
they are expressive enough for many practical uses by adding simple
symmetric lenses to 
the Boomerang language~\cite{boomerang} and applying them to a range of
real-world applications.  This exercise also demonstrates that simple
symmetric lenses can coexist with, and be extended by, other advanced lens features
provided by Boomerang, including {\em quotient
  lenses}~\cite{quotientlenses,maina+:quotient-synthesis} and {\em matching
  lenses}~\cite{matchinglenses}.
